%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Alexis Cruz} % Your name
\address{347-864-8427} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{Mr.Alexiscruz@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf CUNY New York City College of Technology} \hfill {\em January 2013 - December 2018} 
\\ Bachelors of Technology in Computer Systems \\
{\bf GPA:} 3.01 \\
{\bf Relavant Courses:}
\\ \itab{Dynamic Web Programming with JSP}
\\ \itab {Java Applications with Databases}
\\ \itab {Design of Distributed Databases}
\\ \itab{Introduction to Web Programming with HTML and CSS}
\\ \itab {Multi-Media and Mobile Programming with Java}
\\ \itab {Object Oriented System Design}

%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Summary}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Python 3, Java, HTML, CSS, SQL, XML\\
Frameworks & Django, Bootstrap, Bulma \\
Software \& Tools & Excel, LaTeX, SQL/Oracle DBMS, BASH, Android Studio, Netbeans \& Emacs \\
Operating Systems & Windows 7, MacOS, GNU/Linux: Arch Linux, Raspbian \& Ubuntu \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Hearts and Minds}{Manhattan, NY 7/2017 -  8/2017 }{Junior Web Programming Intern}{}
\item Front End development on a campaign website for raising awareness and support for poverty stricken countries.
\item Use of Wordpress and CiviCRM for creating and styling user application forms.
\item Supervised and mentored two high school students in HTML, CSS and programming fundamentals.
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{MAGNET at New York University}{Brooklyn, NY 6/2016 - 8/2016}{Web Programming Intern}{}
\item Assisted on NYU's Ability Project where we worked on making a visually oriented language like Processing accessible with a javascript library p5.js
\item Implemented semantic HTML5 elements to the p5.js website for accessible navigation for the visually disabled using screen readers.
\item Researched various technologies such as ARIA and AJAX for screen reader compatibility. 		
\end{rSubsection}

\begin{rSubsection}{Helen Keller Services for the Blind}{Brooklyn, NY 6/2015 - 8/2015}{Junior Programming Intern}{}
\item Assisted in programming a spreadsheet tool in VBA that would be used for assessing a visually impaired person's skills using Excel.
\item Created various tests such as sorting, filtering, setting formats and creating formulas.
\item Emphasized accessibility, making the spreadsheet easy to navigate with clear labels and instructions.
\item Researched and studied VBA's event-driven properties and implemented those features into the spreadsheet.
\end{rSubsection}
\end{rSection}%   EXAMPLE SECTION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\begin{rSection}{Independent Projects}
{\bf Personal Website CruzPort.com}
\\ Personal website portfolio. Built by using the Django web framework along with Bulma, a responsive CSS framework based on flexbox. I am currently setting 
up a virtual host with Digital Ocean
\\ {\bf Statistical Soccer Database}
\\ Using data scrapped from the internet I populated tables with data for soccer leagues and teams. Currently researching how to integrate APIs for a more accurate data representation for live fixtures.
% \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

\end{rSection}


\end{document}